The transition redshift as a probe of reionization

### 2019-08-11 paper/ms.tex
Add lot more to intro

\section{Introduction}
The redshifted 21~cm line contains a great deal of information about the
structure and evolution of the Epoch of Reionization (EoR). Once measured at
$z\sim6\textup{--}12$, it should reveal the nature of the formation of the
first stars, galaxies, and black holes, as well as the large-scale structure
of the Universe at high redshift \citep{2013fgu..book.....L}. While
instruments have reached the sensitivity necessary to detect the signal during
the EoR, issues of foreground contamination and instrumental artifacts have so
far prevented the success of such efforts. Only upper limits have been placed
on the amplitude of the 21~cm fluctuations \citep[e.g.][]{2013MNRAS.433..639P,
2014PhRvD..89b3002D, 2016ApJ...833..102B, 2017ApJ...838...65P}.

\section{Methods}
\subsection{21cmFAST}
We generate realizations of the 21~cm field for our different EoR models using
the publicly available code \tfast{}
v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST},
commit: \texttt{42e7566}}. Spin temperature fluctuations are computed and the
excursion set approach is used to identify the ionized regions
\citep{2011MNRAS.411..955M}.

>>>>

\section{Introduction} \label{sec:intro}
The redshifted 21~cm line contains a great deal of information about the
structure and evolution of the Epoch of Reionization (EoR). Once measured at
$z\sim6\textup{--}12$, it should reveal the nature of the formation of the
first stars, galaxies, and black holes, as well as the large-scale structure
of the Universe at high redshift \citep{2013fgu..book.....L}. While
instruments have reached the sensitivity necessary to detect the signal during
the EoR, issues of foreground contamination and instrumental artifacts have so
far prevented the success of such efforts. Only upper limits have been placed
on the amplitude of the 21~cm fluctuations \citep[e.g.][]{2013MNRAS.433..639P,
2014PhRvD..89b3002D, 2016ApJ...833..102B, 2017ApJ...838...65P}.

Because of the great difficulties confronting 21~cm auto-spectrum
measurements, the prospect of measuring 21~cm in cross-correlation with
another tracer of large-scale structure, such as galaxies. The galaxy field
will only correlate with the cosmological 21~cm signal, and the foregrounds
will not contribute to the mean signal (though they will make the measurement
noisy, and so some foreground subtraction is still necessary).

The 21~cm-galaxy cross-correlation was first explored by
\citet{2007MNRAS.375.1034W} in the context of using Ly$\alpha$-emitters to
distinguish between ``inside-out'' and ``outside-in'' reionization scenarios.
However, this technique is limited to the late stages of reionization since
Ly$\alpha$-emitters are obscured by neutral hydrogen even slightly earlier
into the EoR \citep[e.g.][]{2006ApJ...648....7K}. \citet{2007ApJ...660.1030F}
expanded upon this by considering a general galaxy survey. It was later shown
that the scale at which the cross-correlation goes from negative to zero (the
``turnover scale'') provides a tracer of the bubble size. However, the precise
turnover scale also depends on the properties of the selected galaxy sample,
with turnover happening on larger scales if only more massive galaxies can be
detected \citep{2009ApJ...690..252L}. A number of authors have studied this
cross-correlation in the context of detectability of the anti-correlation on
large scales \citep{2013MNRAS.432.2615W, 2016MNRAS.457..666V,
2017ApJ...836..176H}, and its dependence on the details of the EoR
\citep{2014MNRAS.438.2474P}.

In addition to the cross-correlation between 21~cm and galaxies, the
cross-correlation between 21~cm and intensity maps has been investigated in an
analogous fashion. Line intensity mapping experiments aim to measure the
large-scale structure of emission in a certain line, and is easier to perform
over a large area at high redshift than a galaxy survey. Current targets
include [\CII], CO, Ly$\alpha$, and H$\alpha$ \citep[for a recent review,
see][]{2017arXiv170909066K}. Another intriguing possible line is [\OIII]
$88\,\mu \text{m}$ \citep[e.g.][]{2018MNRAS.481L..84M}, in which a lensed
$z=9.1$ galaxy has recently shown to be exceptionally bright
\citep{2018Natur.557..392H}.

This cross-correlation was first studied with the CO rotational lines
\citep{2011ApJ...741...70L}, and then the [\CII] \citep{2012ApJ...745...49G}
and Ly$\alpha$ lines \citep{2013ApJ...763..132S}. The possibility of using the
cross-bispectrum the 21~cm and [\CII] fields has been explored
\citep{2018ApJ...867...26B}, along with combining the three cross-spectra with
a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. While in
this work we will only consider the cross-correlation between 21~cm and
galaxies, all of what we consider is applicable to the transition redshift as
computed by cross-correlating 21~cm with any of these emission lines.

In the case of either galaxies or emission lines, it is expected that the two
are positively correlated at the very beginning of the EoR (though the
emission lines may be very weak due to the lack of significant metal
enhancement). This is because the densest regions host the most mass and
therefore 21~cm emission and galaxy populations. However, the densest regions
will also ionize first {\bf cite something}, and after some time 21~cm and
galaxies will become negatively correlated. We refer to the redshift at which
this transition occurs at a fixed $k$ as the ``transition redshift''
$z_\star(k)$, assuming that only one such zero exists. In other words, the
cross-correlation at $k$ vanishes at $z=z_{\star}(k)$.

In this work we investigate to what extent the transition redshift is
dependent upon the galaxy sample used to define it. We assume a galaxy catalog
selected using an [\OIII] emitter survey. In particular, we are interested in
how $z_\star$ changes as we vary the parameters of the [\OIII] luminosity-mass
relation for a fixed halo catalog.

\section{Methods} \label{sec:methods}
\subsection{21cmFAST} \label{ssec:tfast}
We generate realizations of the 21~cm field for our different EoR models using
the publicly available code \tfast{}
v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST},
commit: \texttt{42e7566}}. Spin temperature fluctuations are computed and the
excursion set approach is used to identify the ionized regions
\citep{2011MNRAS.411..955M}.
